An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-11 paper.tex
Added the new figure in the tex file and removed some whitespace.

In addition to the longitudinal perturbations, lateral perturbations were 
also prescribed for a duration of four minutes for one subject in earlier 
trials (6,7,8).  Figure~\ref{fig:lateral_perturbation} shows the effect of the
lateral control of the treadmill by plotting the commanded and measured treadmill
positions. These signals were generated in a similar manner using MATLAB and 
Simulink in which a Gaussian white noise block that twice integrated to obtain the 
lateral position.  The signal was then high-pass filtered with a second-order
Butterworth filter to eliminate drift and then saturated so that the signal 
remained within the 5cm ~\si{\centimeter}lateral  range of the physical hardware.  
The same perturbation signal was used for each of the three trials.

>>>>

In addition to the longitudinal perturbations, lateral perturbations were also
prescribed for a duration of four minutes for one subject in earlier trials
(6,7,8). Figure~\ref{fig:lateral_perturbation} shows the effect of the lateral
control of the treadmill by plotting the commanded and measured treadmill
positions. These signals were generated in a similar manner using MATLAB and
Simulink in which a Gaussian white noise block that twice integrated to obtain
the lateral position. The signal was then high-pass filtered with a
second-order Butterworth filter to eliminate drift and then saturated so that
the signal remained within the 5~\si{\centi\meter} lateral range of the
physical hardware.  The same perturbation signal was used for each of the three
trials.
%
\begin{figure}
  \centering
  \includegraphics{figures/lateral_perturbation.pdf}
  \caption{Commanded treadmill lateral deviation (red) and the recorded
    deviation (blue) for the trials 6, 7, and 8.}
  \label{fig:lateral_perturbation}
\end{figure}
